Extending the WebID Protocol with Access Delegation

### 2012-08-03 paper.tex
upgrade evaluation section

\subsection{MyProfile description}
MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet. Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.

@@

>>>>

As two real-world examples we describe two different implementations where WebID delegation is deployed and needed.
MyProfile is WebID profile service application and OntoWiki a semantic data wiki.

\subsection{MyProfile}
MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Web.
Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{AuthSequence}
  \caption{The MyProfile dashboard visualizes information from different sources fetched by the MyProfile server as a secretary of its user}
  \label{fig:MyProfile}
\end{figure*}

@@

\subsection{OntoWiki}
\todo{Phil: Add OntoWiki general description, the usecases for webid delegation as well as a demonstrating screenshot here}
